Measurement and Analysis of Child Pornography Trafficking on P2P Networks\nocite{Hurley}

### 2013-10-15 Paper_presentation.tex
Mais um pouco...
Dia do Professor
Adicionada parte do Maurício Kubrusly

@@

@@

@@

@@

\caption{Numbers of IP addresses per network sharing FOI} 
\label{tab:table3}
\begin{tabular}{cccc}\hline & \multicolumn{3}{c}{IP Adresses} \\

@@

@@

>>>>

\begin{block}{Background}

@@

\begin{block}{Tools}

\item[\checkmark]A suite of tools, called \textit{RoundUp}\footnote{Strengthening forensic investigations of child pornography on P2P networks\cite{Liberatore}} (deployed by the researchers) has enabled sharing of plain view observations of online CP and associated activities on various networks.

\item[\checkmark]

\item[\checkmark]

@@

\item[\checkmark]Law enforcement’s limited resources and time.

\item[\checkmark]Need triage, focusing on greater impact.

\item[\checkmark]Goal: Decrease the availability of FOI.

@@

\begin{block}{File Redundancy Across GUIDs}

\begin{figure}[!htb]
\centering
\includegraphics[scale=0.5]{FOI_redundancy}
\caption{Count of how many IDs are sharing the same file}.
\label{fig:FOI_redundancy}
\end{figure}

\begin{block}{File Redudancy Across GUIDs}

\item[\checkmark]Low redudancy of FOIs across the GUIDs:
	\begin{itemize}

	\item 90\% of Gnutella files, shared by at most 20 Ids.

\item[\checkmark]Files in common between networks have more redudancy.

\item[\checkmark]Apparently, a good strategy would be to prioritize the users with less redundant FOI.

\begin{block}{File Availability Across Days}

\begin{figure}[!htb]
\centering
\includegraphics[scale=0.5]{FOI_availability}
\caption{Count of days a file has been found online}.
\label{fig:FOI_availability}
\end{figure}

\begin{block}{File Availability Across Days}

\item[\checkmark]Gnutella have a lower availability than eMule:

	\item Only 30\% of Gnutella files are available more than 10 days	.

\item[\checkmark]Files available fewer days, tend to be also less redundant.

\item[\checkmark]Common files also have a greater availability.

@@

\caption{Numbers of IP addresses per network sharing FOI} 
\label{tab:table3}
\begin{tabular}{cccc}\hline & \multicolumn{3}{c}{IP Addresses} \\

@@

\item[\checkmark]Files in U.S mainly. Others countries are underestimated.

\item[\checkmark]No total coverage of files of a certain GUID.

\item[\checkmark]Peers that are rarely online or have few files may have been missed.

\item[\checkmark]Greater number of GUIDs because of different installations.

\item[\checkmark]Peers may have been removed because of police action.

@@

\item[\checkmark]Ecosystems and Underground Economies:

	\item Economic characteristics of Network-based ecosystems.

	\item May explain the irregular use of Tor encountered.

\item[\checkmark]Content Availability in P2P Systems:

	\item Research of general use of P2P.

\item[\checkmark]CP Trafficking in P2P Systems:

	\item Previous work are shallow on understanding how these files are being shared.
